Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2017-11-10 2017-EUROPAR/Gamification/paper.tex
Revising abstract

Distributed computing systems can be created using volunteers who decide to
provide their own  resources or storage to contribute to a common effort. They can, for instance, run a script embedded in a web page, collaboration is straightforward, but also ephemeral, with resources depending on the amount of time a user lends; this  implies that
the user has to be kept engaged so as to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
% NodIO
Anonymous with the objective of discovering rules that encourage volunteer
participation thus increasing the overall computing power. We present the results of
an experiment in which a gamification technique is applied by adding a leader-board
showing the top scores achieved by registered contributors. In the
% NodIO
Anonymous system volunteers can
participate without the need to create an account, so the question was
if the need to register would have a negative impact on user participation.
The experiment results show that even if only a small percentage of users created an account,
those participating in the competition provided around 90\% of the work.

>>>>

Distributed computing systems can be created using volunteers; these
are users who spontaneously, after receiving an invitation, decide to
provide their own resources or storage to contribute to a common
effort. They can, for instance, run a script embedded in a web page;
thus, 
collaboration is straightforward, but also ephemeral, with resources
depending on the amount of time the user decides to lend. This  implies that 
the user has to be kept engaged so as to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
% NodIO
Anonymous with the objective of discovering design decisions that encourage volunteer
participation, thus increasing the overall computing power. We present the results of
an experiment in which a gamification technique is applied by adding a leader-board
showing the top scores achieved by registered contributors. In the
% NodIO
Anonymous system volunteers can
participate without the need to create an account, so one of the
questions we wanted to address was
if the need to register would have a negative impact on user participation.
The experiment results show that even if only a small percentage of users created an account,
those participating in the competition provided around 90\% of the
work, thus effectively increasing the performance of the overall
system.
